---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->
 
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = FALSE,
  comment = "#>",
  fig.path = "README-"
)
```

[![CRAN version](http://www.r-pkg.org/badges/version/spPlot)](http://cran.rstudio.com/web/packages/spPlot/index.html)  
[![GitHub version](https://img.shields.io/badge/GitHub-v`r packageVersion("spPlot")`-brightgreen.svg)](https://github.com/GegznaV/spPlot)
[![Travis-CI Build Status](https://travis-ci.org/GegznaV/spPlot.svg?branch=master)](https://travis-ci.org/GegznaV/spPlot)
[![codecov.io](https://codecov.io/github/GegznaV/spPlot/coverage.svg?branch=master)](https://codecov.io/github/GegznaV/spPlot?branch=master)


  
Development version of package `spPlot` 
==========================================


**The package is under construction.**

Some functions may be changed significantly.

About Documentation
--------------------

Meaning of symbols in function descriptions:

- [+] Well documented function.
- [!], [!!!] Documentation needs attention.
- [!+] Updated function, which was well-documented (some parts may be poor or not documented).
- [.] function may be removed, renamed or changed.


* * *

Install package:

```{r Install package, eval=FALSE}
library(devtools)
install_github("GegznaV/spPlot")
```


* * *

 <p align="right"> 
 File updated on <b>`r Sys.Date()`</b> with version of package  <b>`r packageVersion("spPlot")`</b>
 </p>    


